---
title: "Gas Station Relocation Analysis"
author: "Sangam Patil"
output:
  flexdashboard::flex_dashboard:
    navbar:
      - { icon: "fa-github", href: "https://github.com/Spatial-Data-Analytics-DACSS-690D/Gas-Station-Relocation-Analysis", align: right }

---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar}
#### **Introduction**

This dashboard presents a **Gas Station Relocation Analysis** aimed at identifying and suggesting relocation for fuel stations located within a **200-meter range of schools in Boston**. Using spatial data processing and visualization through **R (ggplot2 + sf)**, the analysis integrates multiple geospatial layers—schools, existing fuel stations, and city boundaries—to detect proximity violations and explore safer, more suitable locations for gas stations.

#### **Plot 1 – Distribution of Fuel Stations in Boston**
This map displays all **existing fuel stations across Boston**, where each point represents a station’s precise location. The color coding helps visualize the **spatial density and spread** of fuel stations across the city, serving as the foundation for later proximity analysis.

#### **Plot 2 – Distribution of Schools in Boston**
This map visualizes **school locations across Boston**, helping identify regions with higher educational density. Overlaying these with fuel station data allows for detecting areas where schools and fuel stations are located in close proximity.

#### **Plot 3 – Fuel Stations Within 200m of Schools**
This visualization highlights **fuel stations that fall within a 200-meter buffer zone** around schools. The color distinction marks which stations are within the restricted range, identifying those that **require relocation consideration** due to safety or zoning concerns.

#### **Plot 4 – Regional Distribution of Fuel Stations**
This bar chart summarizes the **number of fuel stations per region or district** in Boston. It provides a broader view of **fuel infrastructure density**, helping prioritize areas where **relocation or redistribution** efforts may be most necessary.

The GitHub repository linked here contains all code, data, and steps I used to build these maps, ensuring full transparency and reproducibility.



## Column {.tabset .tabset-fade}


### PLOT 1

```{r}
readRDS("plot1.rds")
```

### PLOT 2

```{r}
readRDS("plot2.rds")
```

### PLOT 3

```{r}
readRDS("plot3.rds")
```

### PLOT 4

```{r}
readRDS("plot4.rds")
```

